Using \LaTeX\ to submit manuscripts to peer reviewed journals.

### 2014-02-24 docs/thesis/appendix-test_equations.tex
refactored project. moved libraries

Eq6 & \scriptsize{Fermi Energy} & \scriptsize {\codefont <math> <msub> <mi>E</mi> <mi>F</mi> </msub> <mo>=</mo> <mfrac> <mrow> <msub> <mi>E</mi> <mi>C</mi> </msub> <mo>+</mo> <msub> <mi>E</mi> <mi>V</mi> </msub> </mrow> <mn>2</mn> </mfrac> <mo>+</mo> <mfrac> <mrow> <msub> <mi>κ</mi> <mi>B</mi> </msub> <mi>T</mi> </mrow> <mn>2</mn> </mfrac> <mi>ln</mi> <mfenced close=")" open="("> <mfrac> <msub> <mi>N</mi> <mi>V</mi> </msub> <msub> <mi>N</mi> <mi>C</mi> </msub> </mfrac> </mfenced> </math>} & \scriptsize{$E_F = \frac{E_C + E_V}{2} + \frac{\kappa_{B}T}{2} \ln \left(\frac{N_V}{N_C}\right)$ } \\ \hline

>>>>

Eq6 & \scriptsize{Luminosity of a star in terms of its temperature and radius} & \scriptsize {\codefont <math><mi>L</mi><mo>=</mo><mn>4</mn><mi>π</mi><msup><mi>R</mi><mn>2</mn></msup><mi>σ</mi><msubsup><mi>T</mi><mrow><mi>e</mi><mi>f</mi><mi>f</mi></mrow><mn>4</mn></msubsup></math>
} & \scriptsize{$ L = 4\piR^2\sigma T^4_{eff} $ } \\ \hline
